Analysis of the 2014 Passenger Flight Network

### 2020-02-19 paper/main.tex
removed big images and added new ones

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/united_eigenvalue_centrality.png}
        \caption{
Eigenvalue Centrality of United Airlines}
        \label{fig:united_air_ec}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/delta_eigenvalue_centrality.png}
        \caption{
Eigenvalue Centrality of Delta Airlines}
        \label{fig:delta_air_ec}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/american_eigenvalue_centrality.png}
        \caption{
Eigenvalue Centrality of American Airlines}
        \label{fig:american_air_ec}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/ryan_eigenvalue_centrality.png}
        \caption{
Eigenvalue Centrality of Ryan Air}
        \label{fig:ryan_air_ec}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/southwest_eigenvalue_centrality.png}
        \caption{
Eigenvalue Centrality of Southwest Airlines}
        \label{fig:southwest_air_ec}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/chinasouthern_eigenvalue_centrality.png}
        \caption{
Eigenvalue Centrality of China Southern Airlines}
        \label{fig:chinasouthern_air_ec}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/chinaeastern_eigenvalue_centrality.png}
        \caption{
Eigenvalue Centrality of China Eastern Airlines}
        \label{fig:chinaeastern_air_ec}
\end{figure}

>>>>

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/eigenvector_centrality_distribution.png}
        \caption{
Eigenvector Centrality Distribution}
        \label{fig:eigen_distr}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/closeness_centrality_distribution.png}
        \caption{
Closeness Centrality Distribution}
        \label{fig:closeness_distr}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=80mm]{imgs2/results/geometrical_distance_distribution.png}
        \caption{
Geometrical Distance Distrubution}
        \label{fig:geometric_distr}
\end{figure}
